---
title: "gtsummary in quarto"
format:
  html:
    theme: darkly
execute:
  echo: true
  eval: true
  message: true
  error: true 
---

```{r}
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd",
               "id", "nsibs", "samp", "race_eth", "sex", "region",
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"),
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |>
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes")))
```

# Customization of `tbl_summary()`

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

Characteristics of The National Longitudinal Survey of Youth 1997 (NLSY97) stratified by sex.

```{r}
#| label: tbl-one
#| tbl-cap: "This is a table of a dataframe"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

Here is an example of error in code can be still rendered and show the massage.

- bullet 1

1.  example here

```{r}
#| label: fig-hist
#| fig-cap: "This is a histogram"
hist(rnorm(100))

```

123

`r 7*8`

@fig-hist contains a histogram and @tbl-one a table.

`r scales::number(12868, big.mark = ",")`

```{r}
total_sample <- nrow(nlsy)

# example:
# stats <- list(n = nrow(data),
# 							mean_age = mean(data$age))

#intepretation:
# There were `` `r stats$n` `` participants with a mean age of `` `r stats$mean_age` ``.
```



```{r}
library(gtsummary)
income_table <- tbl_uvregression(
	nlsy,
	y = income,
	include = c(
		sex_cat, race_eth_cat,
		eyesight_cat, income, age_bir
	),
	method = lm
)

inline_text(income_table, variable = "age_bir")
```

```{r}

#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
# igonore, it's for slides #| output-location: slide
table1 <- tbl_summary(
	nlsy,
	by = sex_cat,
	include = c(sex_cat, race_eth_cat, region_cat,
							eyesight_cat, glasses, age_bir)) |>
	add_overall(last = TRUE)
table1

```

```{r exercise 1}
tbl_summary(
	NLSY,
	by = sex_cat,
	include = c(sex_cat, race_eth_cat, region_cat,
							eyesight_cat, glasses, age_bir))
```

```{r exercise 2}
#| label: tbl-two
#| tbl-cap: "This is a table of dataframe comparing people wearing glasses or not"
glass_table <- tbl_summary(
	nlsy,
	by = glasses_cat,
	include = c(age_bir, race_eth_cat, sleep_wknd, region_cat),
	label = list(age_bir ~ "Age", race_eth_cat ~ "Race/Ethnicity", sleep_wknd ~ "Sleep in Weekend", region_cat ~ "Region")
)|>
	add_overall(col_label = "**Total** N ={N}")

#another way Q3
median_weekend_sleep <- median(nlsy$sleep_wknd, na.rm = TRUE)
median_weekend_sleep

inline_text(glass_table, variable = "sleep_wknd", column = "stat_0", pattern="{median}")

```

@tbl-two shows the characteristics of people wear glasses vs people don't 

The median of weekend sleep of the population is `r inline_text(glass_table, variable = "sleep_wknd", column = "stat_0", pattern="{median}")`.


